Examining the impact Overturn of Roe v. Wade: Banning of Abortion on Infant Mortality Rates in the United States Using a Difference-in-Differences Approach

### 2024-11-28 paper/ExaminingtheimpactOverturnofRoev.Wade:BanningofAbortiononInfantMortalityRatesintheUnitedStatesUsingaDifference-in-DifferencesApproach.qmd
update paper with figure title

In this study, we utilized several R packages to streamline data
manipulation, modeling, and visualization. The `tidyverse` package
@tidyverse was central to our workflow, providing tools for data
wrangling and analysis, while `arrow` @arrow efficiently managed parquet
files for larger datasets. We used `modelsummary` package @modelsummary
to generate clean and interpretable summaries of our regression
models.We used `knitr` @knitr and `kableExtra` @kableExtra to generate
clean tables and reproducible reports, and `usmap` for geographical
visualizations. We use `here` @here package simplifies the management of
file paths, ensuring a reproducible workflow by creating a consistent
point of reference for file locations, regardless of the operating
system or working directory. Data cleaning was facilitated by `janitor`
@janitor, while `lubridate` @lubridate handled date-time variables.
Visualization tasks were enhanced with `ggplot2` @ggplot2, and Bayesian
regression modeling was conducted using `rstanarm` @rstanarm. We use `fixest` @fixest to conduct the event study. We use `caret` @caret to conduct the cross-validation of the model. Together, these packages supported an efficient, reproducible workflow for
analyzing and presenting our findings.

@@

```{r}
#| label: fig-eventstudy
#| fig-cap: >
#|   Event Study Analysis of the Impact of Abortion Bans on Infant Mortality Rates in the United   States: 
#|   Evidence Using June 2022 as the Treatment Date and Pre-Treatment (-1, May) as the Reference Period.
#| warning: false
#| echo: false
#| eval: true

>>>>

In this study, we utilized several R packages to streamline data
manipulation, modeling, and visualization. The `tidyverse` package
[@tidyverse] was central to our workflow, providing tools for data
wrangling and analysis, while `arrow` [@arrow] efficiently managed parquet
files for larger datasets. We used `modelsummary` package [@modelsummary]
to generate clean and interpretable summaries of our regression
models.We used `knitr` [@knitr] and `kableExtra` [@kableExtra] to generate
clean tables and reproducible reports, and `usmap` for geographical
visualizations. We use `here` [@here] package simplifies the management of
file paths, ensuring a reproducible workflow by creating a consistent
point of reference for file locations, regardless of the operating
system or working directory. Data cleaning was facilitated by `janitor`
[@janitor], while `lubridate` [@lubridate] handled date-time variables.
Visualization tasks were enhanced with `ggplot2` [@ggplot2], and Bayesian
regression modeling was conducted using `rstanarm` [@rstanarm]. We use `fixest` [@fixest] to conduct the event study. We use `caret` [@caret] to conduct the cross-validation of the model. Together, these packages supported an efficient, reproducible workflow for
analyzing and presenting our findings.

@@

```{r}
#| label: fig-eventstudy
#| fig-cap: >
#|   Event Study Analysis of the Impact of Abortion Bans on Infant Mortality Rates in the United   States: 
#|   Evidence Using June 2022 as the Treatment Date and Pre-Treatment (-1, May 2022) as the Reference Period.
#| warning: false
#| echo: false
#| eval: true
